Natural transformations

### 2017-07-23 papers/base-3/paper-3.tex
added interchange law and some explanation

\section{Equivalence of Categories}
\begin{exmp}
  \[
    \begin{tikzcd}
      \catA: & & \catB:\\
      A \arrow[loop left] & & B \arrow[bend left]{d} \arrow[loop left] \\
                          & & B' \arrow[bend left]{u} \arrow[loop left]
    \end{tikzcd}
  \]
\end{exmp}
%todo explain example

@@

\[
\xymatrix@C+.5em{
\cat{A} \rtwocell<4>^F_G{\alpha}   &
\cat{A}' \rtwocell<4>^{F'}_{G'}{\alpha'}   &
\cat{A}''
}
\]
\[
\xymatrix@C+.5em{
  \cat{A} \rtwocell<4>^{F' \of F}_{G' \of G} &\cat{A}'',
}
\]

This horizontal composition is written $\alpha' * \alpha$.
The following diagram commutes because $\alpha'$ is a natural transformation.
\[
  \begin{tikzcd}
    F'(F(A)) \arrow{r}{F'(\alpha_A)} \arrow{d}{\alpha'_{F(A)}} \arrow{dr}{(\alpha' * \alpha)_A} & F'(G(A)) \arrow{d}{\alpha'_{G(A)}} \\
    G'(F(A)) \arrow{r}{G'(\alpha_A)}                                                            & G'(G(A))
  \end{tikzcd}
\]
So we can define $(\alpha' * \alpha)_A$ either as $G'(\alpha_A) \circ \alpha'_{F(A)}$ or as $\alpha'_{G(A)} \circ F'(\alpha_A)$.
Now we want to show that $\alpha' * \alpha$ is again a natural transformation.
Therefore let $f\from A \to A'$ be a morphism in $\catA$.
\[
  \begin{tikzcd}
    F'(F(A)) \arrow{r}{F'(F(f))} \arrow{d}{\alpha'_{F(A)}} & F'(F(A')) \arrow{d}{\alpha'_{F(A')}} \\
    G'(F(A)) \arrow{r}{G'(F(f))} \arrow{d}{G'(\alpha_A)}   & G'(F(A')) \arrow{d}{G'(\alpha_{A'}}  \\
    G'(G(A)) \arrow{r}{G'(G(f))}                           & G'(G(A'))
  \end{tikzcd}
\]

%todo example

@@

%todo interchange law

>>>>

\section{Equivalence of Categories}
We now want to examine when two categories are the same.
\begin{exmp}
  \[
    \begin{tikzcd}
      \catA: & & \catB:\\
      A \arrow[loop left] & & B \arrow[bend left]{d} \arrow[loop left] \\
                          & & B' \arrow[bend left]{u} \arrow[loop left]
    \end{tikzcd}
  \]
\end{exmp}
todo: explain example

@@

Given two natural transformations $\alpha$ and $\alpha'$:
\[
\xymatrix@C+.5em{
\cat{A} \rtwocell<4>^F_G{\alpha}   &
\cat{A}' \rtwocell<4>^{F'}_{G'}{\alpha'}   &
\cat{A}'',
}
\]
we can obtain a natural transformation:
\[
\xymatrix@C+.5em{
  \cat{A} \rtwocell<4>^{F' \circ F}_{G' \circ G} &\cat{A}'',
}
\]

This horizontal composition is written $\alpha' * \alpha$.
The following diagram commutes because $\alpha'$ is a natural transformation.
\[
  \begin{tikzcd}
    F'(F(A)) \arrow{r}{F'(\alpha_A)} \arrow{d}{\alpha'_{F(A)}} \arrow{dr}{(\alpha' * \alpha)_A} & F'(G(A)) \arrow{d}{\alpha'_{G(A)}} \\
    G'(F(A)) \arrow{r}{G'(\alpha_A)}                                                            & G'(G(A))
  \end{tikzcd}
\]
So we can define $(\alpha' * \alpha)_A$ either as $G'(\alpha_A) \circ \alpha'_{F(A)}$ or as $\alpha'_{G(A)} \circ F'(\alpha_A)$.
Now we want to show that $\alpha' * \alpha$ is again a natural transformation.
Therefore let $f\from A \to A'$ be a morphism in $\catA$.
\[
  \begin{tikzcd}
    F'(F(A)) \arrow{r}{F'(F(f))} \arrow{d}{\alpha'_{F(A)}} & F'(F(A')) \arrow{d}{\alpha'_{F(A')}} \\
    G'(F(A)) \arrow{r}{G'(F(f))} \arrow{d}{G'(\alpha_A)}   & G'(F(A')) \arrow{d}{G'(\alpha_{A'})}  \\
    G'(G(A)) \arrow{r}{G'(G(f))}                           & G'(G(A'))
  \end{tikzcd}
\]

The upper diagram commutes because $\alpha'$ is a natural transformation.
Since $\alpha$ is a natural transformation we have $G(f) \circ \alpha_A = \alpha_{A'} \circ F(f)$.
By applying $G'$ on both sides we obtain the commutativity of the lower diagram.
The commutativity of both inner diagrams ensures the commutativity of the outer diagram.
This shows that $\alpha' * \alpha$ is indeed a natural transformation.

@@

This natural transformations follow the interchange law:
\[
(\beta' \circ \alpha') * (\beta \circ \alpha)
=
(\beta' * \beta) \circ (\alpha' * \alpha)
\from
F' \circ F \to H' \circ H.
\]
Additionally we have $1_{F'} * 1_{F} = 1_{F' \circ F}$, where $1_{F}$ is the natural transformation which components are the identities of $\cat{A'}$.
